---
title: "Data Regression"
author: "Yishan Liu"
date: "November 1, 2015"
output: word_document
---
#Data Analysis about Ozone Data
##Read the data
```{r}
setwd("/Users/Gracie/Desktop/BigData")
mydata<-read.csv("ozone_data.csv")
```
##Create Linear Regression Model 
```{r}
summary(lm(Ozone~Temp+Wind,data=mydata))
```
From the summary we get regression model is as follows:

**$Ozone=-67.3220+1.8276Temp-3.2948Wind$**

The $R^{2}$ value is 0.5611, it is a fair but not a very good model.

##Explore the data by drawing correlation plot and calculate Pearson's correlation coefficient
```{r}
pairs(mydata)
cor(mydata)
```
From the plot and the correlation value, we could see that Wind and Temp have relative greater effects on Ozone value. 
Let's try another model add predictor Temp*Wind
```{r}
summary(model1<-lm(Ozone~Temp+Wind+Temp*Wind,data=mydata))
```
We could see that we had increased the $R^{2}$ by adding the multiplicated predictor. 
```{r}
#Calculate 95% confidence interval
confint(model1,conf.level=0.95)
```
##Hypothesis Test about Ozone value
H0:Value of Ozone in population is >=50
H1:Value of Ozone in population is <50
```{r}
newdata<-mydata[(1)]
t.test(newdata,alternative="less",mu=50)
```
Since P-value 0.006919 is less than alpha=0.05, we should reject the null hypothesis. The Ozone value in population should be less then 50.




